Temporary Trade Barriers: \\ When Will They End?

### 2017-10-27 presentation.tex
change date, etc for SEA presentation

\title[Temporary Trade Barriers: When Will They End?\hspace{2.35in}\insertframenumber/\inserttotalframenumber]{Temporary Trade Barriers: \\ When Will They End?}
\author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University and The Wallis Institute  \newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
\date{May 13, 2016}

@@

\begin{frame}{Why uncertainty?}
\pause
\textbf{Government}
\pause
\begin{itemize}
	\item Renews AD duties if $G$ prefers $\tau^{\mathit{ad}}$ to $\tau^a$
\end{itemize}

>>>>

\title[Temporary Trade Barriers: When Will They End?\hspace{2.35in}\insertframenumber/\inserttotalframenumber]{Temporary Trade Barriers: \\ When Will They End?}
\author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University\newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
\date{November 18, 2017}

@@

\begin{frame}{Why uncertainty?}
\pause
\textbf{Government}
\pause
\begin{itemize}
	\item AD duties renewed if $G$ prefers $\tau^{\mathit{ad}}$ to $\tau^a$
\end{itemize}
